Examining Whether Approximate Visualizations Impact Perception of Corrected Visualizations

### 2016-12-09 paper/paper.tex
Writing

@@

\todo{Daniel: Explain why we see the bias}
\todo{Dom: Talk about massive error}

@@

\todo{Daniel: Statistical methods and outliers}
\todo{Dom: more threats}

>>>>

For question types 2 and 3, the sign of the impact of the expected bias was in the same direction of the bias ($95\% CI 2.594-5.637, 0.329-1.135$ for type 2 and 3, respectively).
This suggests that people tend to be biased in the same direction as the data they see in the approximate visualization.
However, for question type 2, the measured bias was \testit{larger} than the expected bias.
This means that people are reporting answers closer to the approximate visualization than to the precise visualization.
One interpretation of this is that there is a significant bias.
However, we suspect participants remembered very little about the precise data.
Instead we believe this result is heavily influenced by outliers in participant responses.

@@

We are a bit unsure why we see the bias we do.
On one hand, we predicted we would see a bias in the data.
However, we expected the magnitude of the bias would be less than the expected error (e.g., people would be biased only a little by the imprecise visualization).
Instead, we seem to be seeing that people are just not remembering the data they saw.

\todo{Dom: Talk about massive error}

@@

We used linear regression in all of our statistical analyses.
We made this choice because our outcome is numeric rather than categorical.
Additionally, we had no reason to anticipate our data would fit a different distribution.
However, viewing figures \ref{figure_q1}, \ref{figure_q2}, and \ref{figure_q3} shows that although much of the data appears distributed around 0 measured bias, there are many participant responses far away from this value.
These responses do not appear to necessarily be outliers, meaning that many people were answering questions similarly wrong.

Linear regression follows a sum-of-squares approach, and is therefore heavily influenced by values far away from the mean.
Perhaps a different analysis technique is better suited to our data.
We believe our data has systematic problems in how participants are responding to the questions which are unlikely to be corrected by choosing a different statistical test.
However, future studies in this domain should ensure that outliers are being treated in a sensible way.

\todo{Dom: more threats}
